An empirical study of fixation for strategies in the Iterated Prisoner's Dilemma

### 2017-04-25 tex/main.tex
Add more data.

Section~\ref{sec:methodology} will explain the methodological approach used,
Section~\ref{sec:validation} will validate the methodology by comparing
simulated results to analytical results. The main results of this manuscript are
presented in Section~\ref{sec:numerical_results} which will present a detailed
analysis of all the data generated. Finally, Section~\ref{sec:conclusion} will
conclude and offer future avenues for the work presented here.

@@

\section{Numerical results}\label{sec:numerical_results}

Figures~\ref{fig:fixation_heatmap_invade}
and~\ref{fig:fixation_heatmap_coexist} show the fixation rates of each
player on the y axis against each player on the x axis.

@@

Figure~\ref{fig:invasion_boxplot_invade} shows the fixation probabilities for each
strategy when invading another strategy.
Figure~\ref{fig:resistance_boxplot_resist} shows the fixation probabilities for
each strategy when resisting another strategy.
Figure~\ref{fig:coexistance_boxplot_coexist} shows the fixation probabilities for
each strategy when initially coexisting with another strategy.

@@

>>>>

Section~\ref{sec:methodology} will explain the methodological approach used,
Section~\ref{sec:validation} will validate the methodology by comparing
simulated results to analytical results. The main results of this manuscript are
presented in Section~\ref{sec:empirical_results} which will present a detailed
analysis of all the data generated. Finally, Section~\ref{sec:conclusion} will
conclude and offer future avenues for the work presented here.

@@

\section{Empirical results}\label{sec:empirical_results}

\subsection{Strong invaders}\label{sec:strong_invaders}

Figures~\ref{fig:fixation_heatmap_invade} shows the pairwise fitness for
strategies on the columns axis invading a population of strategies on the row
axis.

@@

Figure~\ref{fig:invasion_boxplot_invade} shows the fixation probabilities for each
strategy when invading another strategy.

@@

Figure~\ref{fig:resistance_boxplot_resist} shows the fixation probabilities for
each strategy when resisting another strategy.
Figure~\ref{fig:coexistance_boxplot_coexist} shows the fixation probabilities for
each strategy when initially coexisting with another strategy.
